---
title: "topic_model"
output: html_notebook
---

```{r librarys,echo=FALSE, include=FALSE}
library(quanteda)
library(tidyverse)
library(topicmodels)
library(stm)
library(lubridate)
library(readr)
```


```{r read in data}
# read in dfm from dictionary_method_7000_articles
doc_features <- readRDS("dfm.rds")
corpus <- readRDS("text_corpus.rds")
```

```{r create stm model}
out <- convert(doc_features, to = "stm", docvars = docvars(doc_features))
stm.out <- stm(out$documents, out$vocab, K=16)
# saveRDS(stm.out, "stm_16.rds")
# saveRDS(stm.out, "stm_8.rds")
  
```

For the 16_topic model:

Topic1: Marriage news    
Topic2: Full text unavailable    
Topic3: Best sellers    
Topic4: Travel, advertisement    
Topic5: FIX THIS! No full text but only links and stuff 2019-05-10 (5)    
Topic6: Art -- music and play    
Topic7: Sport, Olympics    
Topic8: Immigrant, travel, Chinatown    
Topic9: International relationship -- south east Asia, Cambodia   
Topic10: International relationship -- Soviet Union -> Iraq War, global containment   
Topic11: Weaponary, machinary   
Topic12: Medicine and education   
Topic13: Index and table of content   
Topic14: Food and recipe   
Topic15: Communist Party issue   
Topic16: Business and trade   



```{r lookinto the meaning of these topics}
stm.out <- readRDS("stm_16.rds")
corpus_df <- as.data.frame(corpus$documents)
text <- corpus_df$texts
findThoughts(stm.out, text, topics = 2, n = 100)
cloud(stm.out, 8)
findTopic(stm.out, "dalai", type = "frex")
```

```{r Visualization of the relationship between topics}
plot.topicCorr(topicCorr(stm.out))
```

```{r}
plot.STM(stm.out)
```

```{r add in the month}
dates <- corpus_df$date
dates <- mdy(dates)
i_month <- month(dates)
i_year <- year(dates)
ym <- 
  paste(i_year, i_month, "01", sep = "-") %>% 
  ymd() %>% 
  as.Date()
  

corpus_df <- 
corpus_df %>% 
  mutate(ym = ym) 

```


```{r Plot the plots about international relationship}

prep <- estimateEffect(c(1:16) ~ s(ym), stm.out, corpus_df)
plot(prep, covariate = "ym", topic = c(1))
plot.estimateEffect(prep, covariate = "ym", method = "continuous", topic=c(9,10,11))

```

```{r Ploting all the topics}
plot.estimateEffect(prep, covariate = "ym", method = "continuous", topic=c(1:16))
```

```{r}
plot.estimateEffect(prep, covariate = "ym", method = "continuous", topic=c(15,16))
```

Topic 15 -- Party issue
Topic 16 -- Business



