---
title: "topic_model"
output: html_notebook
---

```{r librarys}
library(quanteda)
library(tidyverse)
library(topicmodels)
library(stm)
```


```{r read in data}
# read in dfm from dictionary_method_7000_articles
doc_features <- readRDS("dfm.rds")
corpus <- readRDS("text_corpus.rds")
```

```{r create stm model}
out <- convert(doc_features, to = "stm", docvars = docvars(doc_features))
stm.out <- stm(out$documents, out$vocab, K=16)
saveRDS(stm.out, "stm_16.rds")
# saveRDS(stm.out, "stm_8.rds")
  
```

```{r check out the content in each model}
# stm.out <- readRDS("stm_8.rds")
labelTopics(stm.out)
```
For the 8_topic model: 
topic1: music, performance
topic2: cambodia, Russia
topic3: ??
topic4: Food, local
topic5: book...?
topic6: book
topic7: Issue with Tabit
topic8: company and business

For the 16_topic model:

Topic1: Marriage news
Topic2: Full text unavailable
Topic3: Best sellers
Topic4: Travel, advertisement
Topic5: FIX THIS! No full text but only links and stuff 2019-05-10 (5)
Topic6: Art -- music and play
Topic7: Sport, Olympics
Topic8: Immigrant, travel, Chinatown
Topic9: International relationship -- south east Asia, Cambodia 
Topic10: International relationship -- Soviet Union -> Iraq War, global containment 
Topic11: Weaponary, machinary
Topic12: 



```{r lookinto the meaning of these topics}
corpus_df <- as.data.frame(corpus$documents)
text <- corpus_df$texts
findThoughts(stm.out, text, topics = 12, n = 50)
cloud(stm.out, 8)
findTopic(stm.out, "dalai", type = "frex")


```

